---
title: "664project4"
author: "Peter (Tianzhu) Liu"
date: "2022-11-27"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(reticulate)
library(corrplot)
use_python("/usr/local/bin/python3")
```


## Reading in the data
```{r}
# NBA data from 1995-2017
big_data <- read_excel('data.xlsx')
big_data <- big_data[big_data[,"GP"] >= 30,]
head(big_data)


# data <- read.csv(file = 'final_dataset2.csv')
# data = data[data[,"G"] >= 30,]      #screen out less statistically significant data points
# data = data[data[,"Age"] >= 22,]    #salary cap 
# data_reduced = data[,c('X','Player', 'Pos', 'salary','Age','FG.','FT.','MPG','PPG','APG','RPG','TOPG','BPG','SPG')]
# data_reduced = data_reduced[-c(which(data_reduced$Pos == "SF-SG")),]
```

## Split into train and test 80% and 20%
```{r}
set.seed(1234)
# shuffle = sample.int(nrow(data_reduced))
# data_reduced$split = cut(shuffle, breaks = 5, labels = c("1","2","3","4","test"))
# train = subset(data_reduced, split != "test", select = -split)
# test = subset(data_reduced, split == "test", select = -split)
# data_reduced = subset(data_reduced, select = -split)

shuffle = sample.int(nrow(big_data))
big_data$split = cut(shuffle, breaks = 5, labels = c("1", "2", "3", "4", "test"))
train1 = subset(big_data, split != "test", select = -split)
test1 = subset(big_data, split == "test", select = -split)
advanced_train <- train1[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
advanced_train
regular_train <- train1[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
advanced_test <- test1[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
regular_test <- test1[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
```

```{r}
# par(mfrow=c(1,3))
# hist(train$salary,freq = F, main = "Salary", xlab = "Salary")
# hist(log(train$salary),freq = F, main = "Log of Salary", xlab = "Log of Salary")
# hist(sqrt(train$salary),freq = F, main = "Square Root of Salary", xlab = "Square Root of Salary of Salary")

par(mfrow=c(1, 3))
hist(train1$`Salary`,freq = F, main = "Salary", xlab = "%Salary")
hist(log(train1$`Salary`),freq = F, main = "Log of Salary", xlab = "Log of Salary")
hist(sqrt(train1$`Salary`),freq = F, main = "Square Root of Salary", xlab = "Square Root of Salary")
```

```{r}
# model1 = lm(salary~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train)
# summary(model1)
# plot(model1)

# total_model = lm(`% of Cap`~.-(Name + Team + Season), data = big_data)
# summary(total_model)

regular_stats_model = lm(`Salary`~. , data = regular_train)
summary(regular_stats_model)
plot(regular_stats_model)
regular_train
corrplot(cor(regular_train[,]), method = 'number', number.cex = 0.5)
corrplot(cor(advanced_train[,]), method='number', number.cex=0.5)
```

```{r}
advanced_stats_model = lm(`Salary`~., data= advanced_train)
summary(advanced_stats_model)
plot(advanced_stats_model)
```

```{r}
# model2 = lm(log(salary)~ Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train)
# summary(model2)
# plot(model2)

regular_stats_model.log = lm(log(`Salary`)~. , data = regular_train)
summary(regular_stats_model.log)
plot(regular_stats_model.log)
```


```{r}
advanced_stats_model.log = lm(log(`Salary`)~., data= advanced_train)
summary(advanced_stats_model.log)

```

```{r}
# model3 = lm(sqrt(salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train)
# summary(model3)
# plot(model3)

regular_stats_model.sqrt = lm(sqrt(`Salary`)~. , data = regular_train)
summary(regular_stats_model.sqrt)
```

```{r}
advanced_stats_model.sqrt = lm(sqrt(`Salary`)~., data= advanced_train)
summary(advanced_stats_model.sqrt)
```

## Positional value
```{r}
# train_PG =  train[train[,3] == "PG", ]
# train_PF =  train[train[,3] == "PF", ]
# train_SF =  train[train[,3] == "SF", ]
# train_C = train[train[,3] == "C", ]
# train_SG = train[train[,3] == "SG", ]

# test_PG =  test[test[,3] == "PG", ]
# test_PF =  test[test[,3] == "PF", ]
# test_SF =  test[test[,3] == "SF", ]
# test_C = test[test[,3] == "C", ]
# test_SG = test[test[,3] == "SG", ]
```


```{r}
train_PG =train1[train1$Pos == 1,]
train_PF=train1[train1$Pos == 2, ]
train_SF = train1[train1$Pos == 3, ]
train_C = train1[train1$Pos == 4, ]
train_SG = train1[train1$Pos == 5, ]

test_PG =  test1[test1$Pos == 1, ]
test_PF =  test1[test1$Pos == 2, ]
test_SF =  test1[test1$Pos == 3, ]
test_C = test1[test1$Pos == 5, ]
test_SG = test1[test1$Pos == 4, ]

#Regular
train_PG_reg <- train_PG[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
train_SG_reg <- train_SG[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
train_SF_reg <- train_SF[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
train_PF_reg <- train_PF[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
train_C_reg <- train_C[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]

test_PG_reg <- test_PG[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
test_SG_reg <- test_SG[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
test_SF_reg <- test_SF[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
test_PF_reg <- test_PF[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]
test_C_reg <- test_C[,c('Salary','ORPG', 'DRPG', 'RPG', 'APG', 'SPG', 'BPG', 'TPG', 'PFPG', 'PPG', 'FGPG', 'FGAPG', '3PPG', '3PAPG', '2PPG', '2PAPG', 'FTPG', 'FTAPG')]

#Advanced
train_PG_adv <- train_PG[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
train_SG_adv <- train_SG[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
train_SF_adv <- train_SF[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
train_PF_adv <- train_PF[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
train_C_adv <- train_C[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]

test_PG_adv <- test_PG[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
test_SG_adv <- test_SG[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
test_SF_adv <- test_SF[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
test_PF_adv <- test_PF[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]
test_C_adv <- test_C[,c('Salary','PER', 'TS%', '3PAr', 'FTr', 'ORB%', 'DRB%', 'TRB%', 'AST%', 'STL%', 'BLK%', 'TOV%', 'USG%', 'OWS', 'DWS', 'WS', 'WS/48', 'OBPM', 'DBPM', 'BPM', 'VORP')]


```

# First for the PG group

Traditional Statistic Correlation Matrix for Point Guards
```{r}

corrplot(cor(train_PG_reg[,-c(2, 3)]), method = 'number', number.cex = 0.8)
```
Advanced Statistic Correlation Matrix
```{r}
corrplot(cor(train_PG_adv[,]), method="number", number.cex = 0.8)
```


```{r}
par(mfrow=c(2,3))
hist(train_PG$Age,freq = F, main = "Histogram of Age", xlab= "Age")
hist(train_PG$FG.,freq = F, main = "Histogram of Filed Goals per Game", xlab= "Filed Goals per Game")
hist(train_PG$FT.,freq = F, main = "Histogram of Free Throws per Game", xlab= "Free Throws per Game")
hist(train_PG$MPG,freq = F, main = "Histogram of Minutes Played per Game", xlab= "Minutes Played per Game")
hist(train_PG$PPG,freq = F, main = "Histogram of Points per Game", xlab= "Points per Game")
hist(train_PG$APG,freq = F, main = "Histogram of Assits per Game", xlab= "Assits per Game")
hist(train_PG$RPG,freq = F, main = "Histogram of Rebounds per Game", xlab= "Rebounds per Game")
hist(train_PG$TOPG,freq = F, main = "Histogram of Turnovers per Game", xlab= "Turnovers per Game")
hist(train_PG$BPG,freq = F, main = "Histogram of Blocks per Game", xlab= "Blocks per Game")
hist(train_PG$SPG,freq = F, main = "Histogram of Steals per Game", xlab= "Steals per Game")
```

```{r}
lm1_reg = lm(log(train_PG_reg$Salary)~.-(ORPG + DRPG),train_PG_reg)
summary(lm1_reg)
plot(lm1_reg)
```

```{r}
library(car)
library(magrittr)
library(dplyr)
outlierTest(lm1_reg)
influencePlot(lm1_reg)
train_PG_reg <- train_PG_reg %>%  filter(!row_number() %in% c(300, 913, 983, 992, 1025))
```

```{r}
lm2_reg = lm(log(train_PG_reg$Salary)~.-(ORPG + DRPG),train_PG_reg)
summary(lm2_reg)
plot(lm2_reg)
```

```{r}
#AIC and Mallow's Cp select model yields the same model 
library(leaps)
b = regsubsets(log(Salary)~.-(ORPG+ DRPG), data = train_PG_reg, nvmax=13)
rs = summary(b)
rs
plot(1:12,rs$cp, ylab = "CP statistic", xlab = "Number of Parameters")
abline(0,1)

rs$which[which.min(rs$cp),]
lm3 = lm(log(Salary)~RPG+APG+SPG+BPG+TPG+`3PAPG`+`2PPG`+FTPG+FTAPG, data=train_PG_reg)
summary(lm3)
plot(lm3)
#lm3 = lm(log(salary)~Age+FT.+MPG,train2)
#summary(lm3)
#plot(lm3)
```
```{r}
#no sign of heteroscedasticity
library(lmtest)
bptest(lm3, ~ Age*FT.*MPG + I(Age^2) + I(FT.^2) + I(MPG^2), data = train2)
```

```{r}
#not transform a low p-value of heteroscedasticity
lm4 = lm(salary~Age+FT.+MPG,train2)
bptest(lm4, ~ Age*FT.*MPG + I(Age^2) + I(FT.^2) + I(MPG^2), data = train2)
```

```{r}
#no sign of multicollinearity 
library(car)
vif(lm3)
```

Now, remove the MPG, and only consider the skills of the player that might affect his salary. 
```{r}
b = regsubsets(log(salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
lm5 = lm(log(train2$salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG,train2)
#step(lm5)
lm6 = lm(log(salary)~Age+FT.+PPG + RPG,train2)
summary(lm6)
```

```{r}
#compare rmse for original model and reduced model 
rmse=function(x,y){sqrt(mean((x-y)^2))}
rmse(predict(lm2,test_PG),log(test_PG$salary))
rmse(predict(lm3,test_PG),log(test_PG$salary))
rmse(predict(lm6,test_PG),log(test_PG$salary))
predict(lm6, test_PG, interval="predict")
```

-----------------------------------------------------------------------------------------------------------

# Second for the C group,
```{r}
library(corrplot)
corrplot(cor(train_C[,-c(1,2,3)]), method = 'number')
```

```{r}
par(mfrow=c(2,3))
hist(train_C$Age,freq = F, main = "Histogram of Age", xlab= "Age")
hist(train_C$FG.,freq = F, main = "Histogram of Filed Goals per Game", xlab= "Filed Goals per Game")
hist(train_C$FT.,freq = F, main = "Histogram of Free Throws per Game", xlab= "Free Throws per Game")
hist(train_C$MPG,freq = F, main = "Histogram of Minutes Played per Game", xlab= "Minutes Played per Game")
hist(train_C$PPG,freq = F, main = "Histogram of Points per Game", xlab= "Points per Game")
hist(train_C$APG,freq = F, main = "Histogram of Assits per Game", xlab= "Assits per Game")
hist(train_C$RPG,freq = F, main = "Histogram of Rebounds per Game", xlab= "Rebounds per Game")
hist(train_C$TOPG,freq = F, main = "Histogram of Turnovers per Game", xlab= "Turnovers per Game")
hist(train_C$BPG,freq = F, main = "Histogram of Blocks per Game", xlab= "Blocks per Game")
hist(train_C$SPG,freq = F, main = "Histogram of Steals per Game", xlab= "Steals per Game")
```

```{r}
lm1 = lm(log(train_C$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train_C)
summary(lm1)
plot(lm1)
```

```{r}
library(car)
outlierTest(lm1)
influencePlot(lm1)
train2 = subset(train_C, train_C$X != 77 & train_C$X != 97 & train_C$X != 112 & train_C$X != 309 & train_C$X != 333)
```

```{r}
lm2 = lm(log(train2$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train2)
summary(lm2)
plot(lm2)
```

```{r}
#AIC and Mallow's Cp select model yields the same model 
library(leaps)
b = regsubsets(log(salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
plot(2:9,rs$cp, ylab = "CP statistic", xlab = "Number of Parameters")
abline(0,1)
rs$which[which.min(rs$cp),]
#step(lm2)
lm3 = lm(log(salary)~Age + FG. + FT.+ MPG + APG,train2)
summary(lm3)
plot(lm3)
```

```{r}
#no sign of heteroscedasticity
library(lmtest)
bptest(lm3, ~ Age * FG. * FT.* MPG * APG + I(Age^2) + I(FG.^2) + I(FT.^2) + I(MPG^2) + I(APG^2), data = train2)
```

```{r}
#not transform leads to a low p-value of heteroscedasticity
lm4 = lm(salary~Age + FG. + FT.+ MPG + APG,train2)
bptest(lm4, ~ Age * FG. * FT.* MPG * APG + I(Age^2) + I(FG.^2) + I(FT.^2) + I(MPG^2) + I(APG^2), data = train2)
```

```{r}
#no sign of multicollinearity 
library(car)
vif(lm3)
```

Now, remove the MPG, and only consider the skills of the player that might affect his salary. 
```{r}
b = regsubsets(log(salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
lm5 = lm(log(train2$salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG,train2)
#step(lm5)
lm6 = lm(log(salary)~ Age+FG.+FT.+RPG,train2)
summary(lm6)
```

```{r}
#compare rmse for original model and reduced model 
rmse=function(x,y){sqrt(mean((x-y)^2))}
rmse(predict(lm2,test_C),log(test_C$salary))
rmse(predict(lm3,test_C),log(test_C$salary))
rmse(predict(lm6,test_C),log(test_C$salary))
predict(lm6, test_C, interval="predict")
```

-----------------------------------------------------------------------------------------------------------

# Third for the SG group,
```{r}
library(corrplot)
corrplot(cor(train_SG[,-c(1,2,3)]), method = 'number')
```

```{r}
par(mfrow=c(2,3))
hist(train_SG$Age,freq = F, main = "Histogram of Age", xlab= "Age")
hist(train_SG$FG.,freq = F, main = "Histogram of Filed Goals per Game", xlab= "Filed Goals per Game")
hist(train_SG$FT.,freq = F, main = "Histogram of Free Throws per Game", xlab= "Free Throws per Game")
hist(train_SG$MPG,freq = F, main = "Histogram of Minutes Played per Game", xlab= "Minutes Played per Game")
hist(train_SG$PPG,freq = F, main = "Histogram of Points per Game", xlab= "Points per Game")
hist(train_SG$APG,freq = F, main = "Histogram of Assits per Game", xlab= "Assits per Game")
hist(train_SG$RPG,freq = F, main = "Histogram of Rebounds per Game", xlab= "Rebounds per Game")
hist(train_SG$TOPG,freq = F, main = "Histogram of Turnovers per Game", xlab= "Turnovers per Game")
hist(train_SG$BPG,freq = F, main = "Histogram of Blocks per Game", xlab= "Blocks per Game")
hist(train_SG$SPG,freq = F, main = "Histogram of Steals per Game", xlab= "Steals per Game")
```

```{r}
lm1 = lm(log(train_SG$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train_SG)
summary(lm1)
plot(lm1)
```

```{r}
library(car)
outlierTest(lm1)
influencePlot(lm1)
train2 = subset(train_SG, train_SG$X != 8 & train_SG$X != 17 & train_SG$X != 79 & train_SG$X != 145)
```

```{r}
lm2 = lm(log(train2$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train2)
summary(lm2)
plot(lm2)
```

```{r}
#AIC and Mallow's Cp select model yields the same model 
library(leaps)
b = regsubsets(log(salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
plot(2:9,rs$cp, ylab = "CP statistic", xlab = "Number of Parameters")
abline(0,1)
rs$which[which.min(rs$cp),]
#step(lm2)
lm3 = lm(log(salary)~Age + MPG + PPG,train2)
summary(lm3)
plot(lm3)
```

```{r}
#no sign of heteroscedasticity
library(lmtest)
bptest(lm3, ~ Age * MPG * PPG + I(Age^2) + I(MPG^2) + I(PPG^2), data = train2)
```

```{r}
#not transform leads to a low p-value of heteroscedasticity
lm4 = lm(salary~Age +  MPG + PPG,train2)
bptest(lm4, ~ Age * MPG * PPG + I(Age^2) + I(MPG^2) + I(PPG^2), data = train2)
```

```{r}
#not a sign of multicollinearity 
library(car)
vif(lm3)
```

Now, remove the MPG, and only consider the skills of the player that might affect his salary. 
```{r}
b = regsubsets(log(salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
lm5 = lm(log(train2$salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG,train2)
#step(lm5)
lm6 = lm(log(salary)~ Age + PPG,train2)
summary(lm6)
```

```{r}
#compare rmse for original model and reduced model 
rmse=function(x,y){sqrt(mean((x-y)^2))}
rmse(predict(lm2,train_SG),log(train_SG$salary))
rmse(predict(lm3,train_SG),log(train_SG$salary))
rmse(predict(lm6,train_SG),log(train_SG$salary))
predict(lm6, train_SG, interval="predict")
```

-----------------------------------------------------------------------------------------------------------

# Fourth for the PF group,
```{r}
library(corrplot)
corrplot(cor(train_PF[,-c(1,2,3)]), method = 'number')
```

```{r}
par(mfrow=c(2,3))
hist(train_PF$Age,freq = F, main = "Histogram of Age", xlab= "Age")
hist(train_PF$FG.,freq = F, main = "Histogram of Filed Goals per Game", xlab= "Filed Goals per Game")
hist(train_PF$FT.,freq = F, main = "Histogram of Free Throws per Game", xlab= "Free Throws per Game")
hist(train_PF$MPG,freq = F, main = "Histogram of Minutes Played per Game", xlab= "Minutes Played per Game")
hist(train_PF$PPG,freq = F, main = "Histogram of Points per Game", xlab= "Points per Game")
hist(train_PF$APG,freq = F, main = "Histogram of Assits per Game", xlab= "Assits per Game")
hist(train_PF$RPG,freq = F, main = "Histogram of Rebounds per Game", xlab= "Rebounds per Game")
hist(train_PF$TOPG,freq = F, main = "Histogram of Turnovers per Game", xlab= "Turnovers per Game")
hist(train_PF$BPG,freq = F, main = "Histogram of Blocks per Game", xlab= "Blocks per Game")
hist(train_PF$SPG,freq = F, main = "Histogram of Steals per Game", xlab= "Steals per Game")
```

```{r}
lm1 = lm(log(train_PF$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train_PF)
summary(lm1)
plot(lm1)
```

```{r}
library(car)
outlierTest(lm1)
influencePlot(lm1)
train2 = subset(train_PF, train_PF$X != 118 & train_PF$X != 251 & train_PF$X != 262 & train_PF$X != 276 & train_PF$X != 308 & train_PF$X != 458)
```

```{r}
lm2 = lm(log(train2$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train2)
summary(lm2)
plot(lm2)
```

```{r}
#AIC: Age + PPG
#and Mallow's Cp: Age + PPG + APG + RPG + TOPG EXISTS MULTICOOLIENEARITY

library(leaps)
b = regsubsets(log(salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
plot(2:9,rs$cp, ylab = "CP statistic", xlab = "Number of Parameters")
abline(0,1)
rs$which[which.min(rs$cp),]
#step(lm2)
lm3 = lm(log(salary)~Age + PPG,train2)
summary(lm3)
plot(lm3)
```

```{r}
#no sign of heteroscedasticity
library(lmtest)
bptest(lm3, ~ Age * PPG + I(Age^2) + I(PPG^2) , data = train2)
```

```{r}
#not transform
lm4 = lm(salary~Age + PPG ,train2)
bptest(lm4, ~ Age * PPG + I(Age^2) + I(PPG^2), data = train2)
```

```{r}
#no sign of multicollinearity 
library(car)
vif(lm3)
```

Now, remove the MPG, and only consider the skills of the player that might affect his salary. 
```{r}
b = regsubsets(log(salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
lm5 = lm(log(train2$salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG,train2)
#step(lm5)
lm6 = lm(log(salary)~ Age+PPG+APG+RPG+TOPG,train2)
summary(lm6)
```

```{r}
#compare rmse for original model and reduced model 
rmse=function(x,y){sqrt(mean((x-y)^2))}
rmse(predict(lm2,train_PF),log(train_PF$salary))
rmse(predict(lm3,train_PF),log(train_PF$salary))
rmse(predict(lm6,train_PF),log(train_PF$salary))
predict(lm6, train_PF, interval="predict")
```

-----------------------------------------------------------------------------------------------------------

# Finally for the SF group, need to proceed with caution because data point is few
```{r}
library(corrplot)
corrplot(cor(train_SF[,-c(1,2,3)]), method = 'number')
```

```{r}
par(mfrow=c(2,3))
hist(train_SF$Age,freq = F, main = "Histogram of Age", xlab= "Age")
hist(train_SF$FG.,freq = F, main = "Histogram of Filed Goals per Game", xlab= "Filed Goals per Game")
hist(train_SF$FT.,freq = F, main = "Histogram of Free Throws per Game", xlab= "Free Throws per Game")
hist(train_SF$MPG,freq = F, main = "Histogram of Minutes Played per Game", xlab= "Minutes Played per Game")
hist(train_SF$PPG,freq = F, main = "Histogram of Points per Game", xlab= "Points per Game")
hist(train_SF$APG,freq = F, main = "Histogram of Assits per Game", xlab= "Assits per Game")
hist(train_SF$RPG,freq = F, main = "Histogram of Rebounds per Game", xlab= "Rebounds per Game")
hist(train_SF$TOPG,freq = F, main = "Histogram of Turnovers per Game", xlab= "Turnovers per Game")
hist(train_SF$BPG,freq = F, main = "Histogram of Blocks per Game", xlab= "Blocks per Game")
hist(train_SF$SPG,freq = F, main = "Histogram of Steals per Game", xlab= "Steals per Game")
```

```{r}
lm1 = lm(log(train_SF$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train_SF)
summary(lm1)
plot(lm1)
```

```{r}
library(car)
outlierTest(lm1)
influencePlot(lm1)
train2 = subset(train_SF, train_SF$X != 235 & train_SF$X != 254 & train_SF$X != 264 & train_SF$X != 350)
```

```{r}
lm2 = lm(log(train2$salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG,train2)
summary(lm2)
plot(lm2)
```

```{r}
#AIC and Mallow's Cp select model yields the same model 
library(leaps)
b = regsubsets(log(salary)~Age+FG.+FT.+MPG+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
plot(2:9,rs$cp, ylab = "CP statistic", xlab = "Number of Parameters")
abline(0,1)
rs$which[which.min(rs$cp),]
#step(lm2)
lm3 = lm(log(salary)~Age + PPG + RPG + BPG,train2)
summary(lm3)
plot(lm3)
```

```{r}
#no sign of heteroscedasticity
library(lmtest)
bptest(lm3, ~ Age * PPG * RPG * BPG + I(Age^2) + I(PPG^2) + I(RPG^2) + I(BPG^2), data = train2)
```

```{r}
#not transform 
lm4 = lm(salary~Age + PPG + RPG + BPG,train2)
bptest(lm4, ~ Age * PPG * RPG * BPG + I(Age^2) + I(PPG^2) + I(RPG^2) + I(BPG^2), data = train2)
```

```{r}
#no sign of multicollinearity 
library(car)
vif(lm3)
```

Now, remove the MPG, and only consider the skills of the player that might affect his salary. 
```{r}
b = regsubsets(log(salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG, data = train2)
rs = summary(b)
lm5 = lm(log(train2$salary)~Age+FG.+FT.+PPG+APG+RPG+TOPG+BPG+SPG,train2)
#step(lm5)
lm6 = lm(log(salary)~ Age + PPG + RPG + BPG,train2)
summary(lm6)
```

```{r}
#compare rmse for original model and reduced model 
rmse=function(x,y){sqrt(mean((x-y)^2))}
rmse(predict(lm2,train_SF),log(train_SF$salary))
#rmse(predict(lm3,train_SF),log(train_SF$salary))
rmse(predict(lm6,train_SF),log(train_SF$salary))
predict(lm6, train_SF, interval="predict")
```

